Universal Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-30 SI.tex
Add SI part to the anisotropy data

\section{Raw data from first principles calculations}
\subsection{Quantities from First Principles Calculation}
\label{sec:raw}

@@

\subsection{Bandstructures of 2D Materials Calculated}
\label{sec:bs}

>>>>

\subsection{Comparing dielectric anisotropy}
The dielectric anisotropy $\eta$ proposed in the main text is also
applied to other dimensions. Similar to the case of 2D and bulk
layered materials, $\epsilon$ is used to compare the anisotropy when
the material is periodic in all dimensions (bulk covalent materials),
while the polarizability $\alpha$ is used for reduced dimensional
materials.

The following types materials are chosen for comparison:
\begin{itemize}
\item Bulk covalent materials.  \\
  The list of materials and bandgap are chosen according to
  Ref. \citenum{sze_appendix_2006}, including IV-IV, III-V, II-VI, and
  IV-VI semiconductors. All these materials have isotropic dielectric
  properties.
\item Planar OSc \\
  The planar OScs include metal phthanocyanines, disk-like polycyclic
  aromatic hydrocarbon (PAHs), and benzene derivatives. The
  dimensionality of these materials are close to 2D materials due to
  their planar shape. The bandgap values (mostly at B3LYP density
  functional with 6-31G** basis sets) are extracted from the NIST
  Computational Chemistry Comparison and Benchmark Database
  (http://cccdb.nist.gov, Release 19, April 2018) and the
  polarizability values are obtained from
  Refs. \citenum{Miller_1990,Ramprasad_2006}.
\item Carbon nanotubes (CNT) \\
  Like 2D materials, CNTs are periodic along the 1D directions, and
  shoudl be treated in a similar way to get the polarizability
  proportional to [Length]$^{2}$ \cite{Benedict_1995}. Semiconducting
  zigzag and armchair CNTs are considered, with their electronic
  properties obtained from Refs
  \citenum{Benedict_1995,Matsuda_2010}. and dielectric properties
  obtained from
  Refs. \citenum{Benedict_1995,Jensen_2000,Brothers_2008}.
\item Linear OSc \\
  We choose the polyacenes (linear PAHs from benznene to nonacene) as
  a model system of linear OScs. The bandgaps are obtained from
  \citenum{Salzner_1998} and the polarizabilities are obtained from
  \citenum{Hinchliffe_2005}.
\item Fullerenes \\
  The bandgap of fullerens (C$_{n}$ where $n=60*m^{2}$ where
  $m=1\sim{}7$) are taken from \citenum{Lin_1994} and the
  polarizabilities are taken from \citenum{Martin_2008}. All these
  materials have isotropic polarizability due to the high symmetry.
\end{itemize}

\section{Raw data from first principles calculations}
\subsection{Quantities from first principles calculation}
\label{sec:raw}

@@

\subsection{Bandstructures of 2D materials calculated}
\label{sec:bs}
